Article Title

### 2013-07-29 sections/Abstract.tex
Added figure captions.
minor changes

Correlations between the spiking activity of pairs of neurons are among the most familiar descriptive statistics of neural activity. Multineuronal recordings provide richer information than the equivalent number of neuron pairs. For example, the full covariance matrix reveals correlated activity across the entire population as well as partial correlations between pairs.  Estimation of covariance matrices can be improved by regularization, \emph{i.e.}\;by imposing some kind of structure.  Optimal regularization must be determined empirically since its effect depends on how closely the imposed structure matches the underlying regularities. For example, we can use low-rank parameterizations of the covariance matrix to account for common fluctuations across the recorded population. Conversely, if correlations are strongly influenced by a small fraction of pairwise linear associations between the observed neurons, we can impose sparsity on the inverse covariance matrix. We can also use a `sparse+low rank’ inverse covariance representation to account for both common fluctuations and pairwise interactions.

>>>>

Correlations \TODO{we assume readers understand that Pearson linear correlations are meant here} between the spiking activity of pairs of neurons are among the most familiar descriptive statistics of neural activity. Multineuronal recordings provide richer information than the equivalent number of neuron pairs. For example, the full covariance \TODO{we assume readers understand the relationship between covariance and correlation} matrix reveals correlated activity across the entire population as well as partial correlations between pairs.  Estimation of covariance matrices can be improved by regularization, \emph{i.e.}\;by imposing some kind of structure.  Optimal regularization must be determined empirically since its effect depends on how closely the imposed structure matches the underlying regularities. For example, we can use low-rank parameterizations of the covariance matrix to account for common fluctuations across the recorded population. Conversely, if correlations are strongly influenced by a small fraction of pairwise linear associations between the observed neurons, we can impose sparsity on the inverse covariance matrix. We can also use a `sparse+low rank' inverse covariance representation to account for both common fluctuations and pairwise interactions.

### 2013-07-29 sections/Acquisition.tex
Added figure captions.
minor changes

\subsection{Data acquisition}
Describe the two-photon experiment, refer to Fig.\;1

>>>>

\subsection{Data acquisition}
Describe the two-photon experiment, refer to Fig.\;1.

\textbf{Figure 1.}{
Experimental setup and data acquisition. 
\textbf{A}: Mouse in two-photon microscope, visual stimulation, 3D scanning of cells.
\textbf{B}: Calcium signals
\textbf{C}: Deconvolution and binning.
}\label{fig:01}
